---
title: "Assignment 5"
author: "Nathan Redon"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Exploratory Figure
I start by taking a look at the data and choosing two variables I'm interested in. I want to see how things vary by location and decided that the depth the fish were taken from could be fun to look at.  
```{r make.expl.fig, include = TRUE}
## Dependencies
if(!require("here")){
    install.packages("here")
    library(here)
}

## Get data
df <- read.csv(here("data","siscowet.csv"))

## Wrangle data
df$wgt[541] <- 1580 # "Fix" the crazy outlier just for this assignment
df$locID <- as.factor(df$locID)

## Make exploratory figure, how did sample depth vary by location?
jpeg("exploratory_fig.jpg") # open file
plot(pnldep ~ locID, data = df) # Check out depth, looks like there's some variability

# save plot
dev.off() # close file
```
  
## Expository figure
I then wanted to clean this up and try out a bunch of new things with ggplot (since I've only used Base R to make graphs so far).  

All in all, I think it's pretty cheesy and I definitely need to change the yellow but I've spent enough time on it already!  
```{r make.expo.fig, include = TRUE}
## Dependencies
if(!require("here")){
    install.packages("here")
    library(here)
}

if(!require("ggplot2")){
    install.packages("ggplot2")
    library(ggplot2)
}

if(!require("ggtext")){
    install.packages("ggtext")
    library(ggtext)
}

## Get data
df <- read.csv(here("data","siscowet.csv"))

## Wrangle data
df$wgt[541] <- 1580 # "Fix" the crazy outlier just for this assignment
df$locID <- as.factor(df$locID)

## Make expository figure
# reorder factor levels by length to best represent spread
df$locID = with(df, reorder(locID, len))

# get axis labels sorted
fig.loc1 <- here("figures","axis_labels","fb1.png")
fig.loc2 <- here("figures","axis_labels","fb2.png")
fig.loc3 <- here("figures","axis_labels","fb3.png")
fig.loc4 <- here("figures","axis_labels","fb4.png")
labels <- c(
  fb1 <- paste0("<img src='",fig.loc1,"' width='30' />"),
  fb2 <- paste0("<img src='",fig.loc2,"' width='30' />"),
  fb3 <- paste0("<img src='",fig.loc3,"' width='30' />"),
  fb4 <- paste0("<img src='",fig.loc4,"' width='30' />")
)

# draw plot
p <- ggplot(df, aes(x = factor(locID), y = pnldep)) # depth by location
p + geom_violin(aes(fill = locID)) + # make violin plot
    scale_fill_viridis_d() + # Viridis colorset
    scale_x_discrete(name = NULL, position = "top", labels = labels) + # Handle x-axis pos and labels
    expand_limits(x = 0, y = 0) + # Set origin to 0,0
    ylab("Gillnet\npanel\ndepth(m)") + # Make y label lines per word
    # Make title labels
    labs(color = "Penguin Species", 
         title = "<b>Variability in gillnet panel depth targeting Siscowet Lake Trout in Lake Superior across four sites</b><br>
           <span style = 'font-size:10pt'><span       style='color:#410155'>Grand Marais</span>, <span style='color:#3A6890'>Deer Park </span>, <span style='color:#4DB777'>Blind Sucker</span>, and <span style='color:#FAE600'>Little Lake Harbor</span>.</span><br>")+
    scale_y_reverse() + # Flip the y-axis to make depth chart
    theme_minimal() + # Minimal theme
    theme(
      plot.title.position = "panel", # Put title over plot
      plot.title = element_textbox_simple(size=12), # Plot font types
      axis.title.x = element_blank(), # No x-axis title
      axis.ticks.x = element_blank(), # No x-axis ticks
      axis.text.x.top = element_markdown(), # x-axis labels exist
      axis.title.y = element_text(angle = 0, vjust = .6,size=14), # Y-axis label font
      axis.text = element_text(size=12), # Default axis font
      legend.position="none") # No legend

# save plot
ggsave("expository_fig.jpg")

```

